\section{Conclusion}
\label{sec:-conc}

In this paper, we examine a number of machine learning algorithms as 
they apply to the problem of classifying forest cover based on 
cartographic variables.  We specify accuracy both for naive solutions 
(before tuning), and for solutions with more carefully tuned 
hyperparameters.  The final collection of k-Nearest Neighbor, Support 
Vector Machine, Gradient Boosting Machine, and Random Forest result in 
a significant increase in accuracy over the next best approach, at a 
final accuracy of 80\%.

In the course of our experimentation, we discovered a number of 
interesting relationships between the variables in the feature set.  
We were able to make use of some of these relationships, by introducing 
new featuers while transforming others, but some of the correlations 
between features remains a mystery. If we had the opportunity to 
continue work on this project, we would like to undertake a more 
comprehensive and formal analysis of the data.  

For instance, what 
kind of relationship exists between the vairous Hillshade values?  
How closely correlated are they with Elevation?  We have a great 
many soil types, but some of them seem to overlap. Do all soil types 
classified as ``extremely stony'' occur with similar environments, 
regardless of whether the soil is Bross family or Leighcan-Moran family?  
We would be interested in answering these questions and more, perhaps 
in consultation with an actual expert in the domain of geology.






%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "main"
%%% End: 
